---
title: "2b_social_spatial_predicting_microbiome_similarity"
author: "Holly Neille"
date: "2024-05-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load libraries
```{r}
library(brms)
```

## Social association and spatial proximity predicting microbiome similarity
I constructed a dyadic Bayesian betaregression models predicting microbiome Jaccard similarity with social association, spatial association and dyadic covariates (sex similarity, age similarity, temporal distance between samples collected and read depth difference). I included multi-membership random effects to account for non-independence of the response variable, Jaccard similarity, where the same individuals or samples are in multiple dyads. 

```{r}
soc_spa_micr <- readRDS("msim_spa_12_all_rd2_rerun2.rds")
summary(soc_spa_micr)
```

## Phenotypically subsetting microbiome
Anaerobic microbiome
```{r}
soc_spa_micr_ana <- readRDS("msim_spa_12_all_ana.rds")
summary(soc_spa_micr_ana)
```

Aerotolerant microbiome
```{r}
soc_spa_micr_aer <- readRDS("msim_spa_12_all_aer.rds")
summary(soc_spa_micr_aer) # no issues with divergent transitions here or adapt_delta as the models run with these issues fixed in Raulo et al., 2024 had the same model estimates and significance.
```

