---
title: "social_centrality_predicting_microbiome_richness"
author: "Holly Neille"
date: "2024-05-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load in libraries 
```{r}
library(brms)
```

## Social centrality predicting parasitome richness
Separate Bayesian Poisson regression models were constructed to predict microbiome richness (number of unique ASVs) with each social centrality metric. I included covariates (sex-reproductive status, age, month, read depth) and the random effect (individual ID). All centrality metrics were scaled between 0 and 1 to allow for comparison of effect sizes. 

#### Overall microbiome
Degree
```{r}
deg_mrich <- readRDS("m1d_ALL_s2.rds")
summary(deg_mrich)
```

Strength
```{r}
str_mrich <- readRDS("m1s_ALL_s2.rds")
summary(str_mrich)
```

Eigenvector centrality
```{r}
eig_mrich <- readRDS("m1e_ALL.rds") # eigenvector range is between 0 and 1
summary(eig_mrich)
```

Betweeenness
```{r}
bet_mrich <- readRDS("m1b_ALL_s2.rds")
summary(bet_mrich)
```

Bridge propensity
```{r}
bp_mrich <- readRDS("m1bp_ALL_s2.rds")
summary(bp_mrich)
```

Clustering coefficient
```{r}
cc_mrich<- readRDS("m1cc_ALL_s2.rds")
summary(cc_mrich)
```

#### Anaerobic microbiome
Degree
```{r}
deg_mrich_ana <- readRDS("m1d_ana_s2.rds")
summary(deg_mrich_ana)
```

Strength
```{r}
str_mrich_ana <- readRDS("m1s_ana_s2.rds")
summary(str_mrich_ana)
```

Eigenvector centrality
```{r}
eig_mrich_ana <- readRDS("m1e_anaerobes_2.rds") # eigenvector range is between 0 and 1
summary(eig_mrich_ana)
```

Betweeenness
```{r}
bet_mrich_ana <- readRDS("m1b_ana_s2.rds")
summary(bet_mrich_ana)
```

Bridge propensity
```{r}
bp_mrich_ana <- readRDS("m1bp_ana_s2.rds")
summary(bp_mrich_ana)
```

Clustering coefficient
```{r}
cc_mrich_ana<- readRDS("m1cc_ana_s2_2.rds")
summary(cc_mrich_ana)
```


#### Aerotolerant microbiome
Degree
```{r}
deg_mrich_aer <- readRDS("m1d_aer_s2.rds")
summary(deg_mrich_aer)
```

Strength
```{r}
str_mrich_aer <- readRDS("m1s_aer_s2.rds")
summary(str_mrich_aer)
```

Eigenvector centrality
```{r}
eig_mrich_aer <- readRDS("m1e_aer.rds") # eigenvector range is between 0 and 1
summary(eig_mrich_aer)
```

Betweeenness
```{r}
bet_mrich_aer <- readRDS("m1b_aer_s2.rds")
summary(bet_mrich_aer)
```

Bridge propensity
```{r}
bp_mrich_aer <- readRDS("m1bp_aer_s2.rds")
summary(bp_mrich_aer)
```

Clustering coefficient
```{r}
cc_mrich_aer<- readRDS("m1cc_aer_s2_2.rds")
summary(cc_mrich_aer)
```


