---
title: "social_centrality_and_parasitome_richness"
author: "Holly Neille"
date: "2024-05-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load in libraries 
```{r}
library(brms)
```

## Social centrality predicting parasitome richness
Separate Bayesian Poisson regression models were constructed to predict parasitome richness (number of gut parasite taxa) with each social centrality metric. I included covariates (sex-reproductive status, age, month, faecal sample mass) and the random effect (individual ID). All centrality metrics were scaled between 0 and 1 to allow for comparison of effect sizes. 

Degree
```{r}
deg_prich <- readRDS("d_pois_scaled.rds")
summary(deg_prich)
```

Strength
```{r}
str_prich <- readRDS("s_pois_scaled.rds")
summary(str_prich)
```

Eigenvector centrality
```{r}
eig_prich <- readRDS("e_pois_filt.rds") # eigenvector range is between 0 and 1
summary(eig_prich)
```

Betweeenness
```{r}
bet_prich <- readRDS("bet_pois_scaled2.rds")
summary(bet_prich)
```

Bridge propensity
```{r}
bp_prich <- readRDS("bp_pois_scaled3.rds")
summary(bp_prich)
```

Clustering coefficient
```{r}
cc_prich<- readRDS("cc_pois_s3.rds")
summary(cc_prich)
```

