---
title: "social_centrality_predicting_parasite_infection"
author: "Holly Neille"
date: "2024-05-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load relevant libraries
```{r}
library(brms)
```

## Social centrality predicting parasite infection status (0/1)
Separate Bayesian Bernouilli regression models predicted parasite infection status with each social centrality metric (due to potential covariance between social centrality metrics). I included the covariates (sex-reproductive status and faecal mass) and random effect of individual ID. Due to sample size limitations, including age and month resulted in model convergence so I did not include these covariates. 

Degree
```{r}
deg_TINF <- readRDS("TINF_d4.rds")
summary(deg_TINF)
```

Strength
```{r}
str_TINF <- readRDS("TINF_s_2.rds")
summary(deg_TINF)
```

Eigenvector centrality
```{r}
eig_TINF <- readRDS("TINF_e2.rds")
summary(deg_TINF)
```

Betweenness
```{r}
bet_TINF <- readRDS("TINF_b_2.rds")
summary(deg_TINF)
```

Bridge propensity
```{r}
bp_TINF <- readRDS("TINF_bp2.rds")
summary(deg_TINF)
```

Clustering coefficient 
```{r}
cc_TINF <- readRDS("TINF_cc_2.rds")
summary(deg_TINF)
```

## Social centrality predicting parasite taxa-specific infection status (0/1)
Separate Bayesian Bernouilli regression models predicted infection status with prevalent parasite taxa (prevalence>15%) with each social centrality metric (due to potential covariance between social centrality metrics). I included the covariates (sex-reproductive status and faecal mass) and random effect of individual ID. Due to sample size limitations, including age and month resulted in model convergence so I did not include these covariates. 

#### H. polygyrus
Degree 
```{r}
hpol_deg <- readRDS("hpol_INF_d.rds")
summary(hpol_deg)
```

Strength
```{r}
hpol_str <- readRDS("hpol_INF_s.rds")
summary(hpol_str)
```

Eigenvector centrality
```{r}
hpol_eig <- readRDS("hpol_INF_e.rds")
summary(hpol_eig)
```

Betweenness
```{r}
hpol_bet <- readRDS("hpol_INF_b.rds")
summary(hpol_bet)
```

Bridge propensity
```{r}
hpol_bp <- readRDS("hpol_INF_bp.rds")
summary(hpol_bp)
```

Clustering coefficient
```{r}
hpol_cc <- readRDS("hpol_INF_cc.rds")
summary(hpol_cc)
```

#### Aonchotheca sp. 
Degree 
```{r}
aonc_deg <- readRDS("cap_INF_d.rds")
summary(aonc_deg)
```

Strength
```{r}
aonc_str <- readRDS("cap_INF_s.rds")
summary(aonc_str)
```

Eigenvector centrality
```{r}
aonc_eig <- readRDS("cap_INF_e.rds")
summary(aonc_eig)
```

Betweenness
```{r}
aonc_bet <- readRDS("cap_INF_b.rds")
summary(aonc_bet)
```

Bridge propensity
```{r}
aonc_bp <- readRDS("cap_INF_bp.rds")
summary(aonc_bp)
```

Clustering coefficient
```{r}
aonc_cc <- readRDS("cap_INF_cc.rds")
summary(aonc_cc)
```

#### Eimeria spp. 
Eimeria spp. infection status encompasses infection status for either E. apionodes, E. hungaryensis or E. uptoni. Sample size was too small to investigate separate Eimeria species. 

Degree 
```{r}
eim_deg <- readRDS("deg_EIM_d.rds")
summary(eim_deg)
```

Strength
```{r}
eim_str <- readRDS("str_EIM.rds")
summary(eim_str)
```

Eigenvector centrality
```{r}
eim_eig <- readRDS("eig_EIM.rds")
summary(eim_eig)
```

Betweenness
```{r}
eim_bet <- readRDS("bet_EIM.rds")
summary(eim_bet)
```

Bridge propensity
```{r}
eim_bp <- readRDS("bp_EIM.rds")
summary(eim_bp)
```

Clustering coefficient
```{r}
eim_bp <- readRDS("cc_EIM.rds")
summary(eim_bp)
```
